Foregrounds in Fourier Space for Redshifted 21~cm Observatories

### 2015-02-04 ms.tex
Add new section "Foreground Model"
from ed945db:
============

Add figure4.eps to git version control

In ms.tex,

(*) Add new section "Foreground Model"
(*) Minor modification to last paragraph of section 2.1

In our present study, we use an antenna layout identical to that of the MWA \citep{bea12}. The array is arranged as a centrally condensed core of $\sim$~300~m --- there are many spacings in the range 5--50~m --- and a radial density that falls off as the inverse of the radius, with the longest baselines at 3~km. Here we focus on antenna spacings $|\boldsymbol{b}| \le 200$~m (spatial scales relevant to reionization). For geometrical intuition, we restrict the orientation ($\theta_b$, measured anti-clockwise from East) of all baselines to lie in the range $-67.5\arcdeg \leq \theta_b < 112.5\arcdeg$. Baselines oriented in the other half--plane measure conjugate visibilities with delays of equal magnitude but of opposite sign and hence are ignored in our analysis. {\bf Note that visibilities from different baselines have not been averaged together in this analysis}.

@@

>>>>

In our present study, we use a latitude (-26.701\arcdeg) and an antenna layout identical to that of the MWA \citep{bea12}. The array is arranged as a centrally condensed core of $\sim$~300~m --- there are many spacings in the range 5--50~m --- and a radial density that falls off as the inverse of the radius, with the longest baselines at 3~km. Here we focus on antenna spacings $|\boldsymbol{b}| \le 200$~m (spatial scales relevant to reionization). For geometrical intuition, we restrict the orientation ($\theta_b$, measured anti-clockwise from East) of all baselines to lie in the range $-67.5\arcdeg \leq \theta_b < 112.5\arcdeg$. Baselines oriented in the other half--plane measure conjugate visibilities with delays of equal magnitude but of opposite sign and hence are ignored in our analysis. {\bf Note that visibilities from different baselines have not been averaged together in this analysis}.

@@

In wide--field measurements, it is important to consider an all--sky model for foreground objects in evaluating the features seen in the power spectrum instead of restricting only to the primary field of view. We use a foreground model that includes both diffuse and bright compact components.

For the diffuse component, we use an all--sky radio foreground model \citep{deo08} to estimate the emission at 185~MHz. At this frequency, since this map is predominantly based on the 408~MHz map of \citet{has82} which has an angular resolution of 0.85\arcdeg, we smoothed the 185~MHz map to the same resolution. However, to avoid any artifacts from sampling this map, we sample it at $\approx 27$\arcmin~intervals. We model the diffuse foreground spectra with a spectral index at each pixel in the map, estimated from model maps at 170~MHz and 200~MHz.

From the SUMSS catalog, we select objects whose deconvolved major axes are equal to 0\arcsec, thereby strictly selecting point sources. From the NVSS catalog, we excluded objects that overlap with those in the SUMSS survey footprint. Point sources from NVSS were selected if the convolved major axes were not greater than $\approx 47$\arcsec, which matches the angular resolution of the survey. Using a mean spectral index of $\langle\alpha_\textrm{sp}\rangle=-0.83$ (flux density, $S(f)\propto f^{\alpha_\textrm{sp}}$) obtained by \citet{mau03} for both NVSS and SUMSS catalog objects, we calculate the corresponding flux densities at 185~MHz, $S_{185}$. From this subset, we choose point sources with $S_{185}\geq 10$~Jy. The selection of such bright point sources is not affected by minor differences in flux density sensitivity of the two surveys. We verified that our selection criteria ensure a similar areal density of objects in the two surveys.

Based on these criteria, we selected 100 objects from the SUMSS catalog and 250 objects from the NVSS catalog. Together with the diffuse foreground model, we obtain an all--sky foreground model consisting of both compact and diffuse emission. Figure~\ref{fig:sky-model-generic} shows the diffuse (top) and compact (bottom) foreground emission model used in our study. In this snapshot at 0.09~hours LST, the Galactic center in the diffuse model appears to have just set in the West.

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figure4.eps}
\caption{Foreground model at 185~MHz consisting of diffuse emission (top) and bright point sources (bottom) visible during a snapshot at 0.09~hours LST. In the diffuse model, the Galactic center appears to have just set in the West. \label{fig:sky-model-generic}}
\end{figure}
